The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-07-11 paper.tex
Began Syllable Contact section

>>>>

\subsection{Syllable Contact}

The alternative markedness-based approach to sonority-driven epenthesis that I will explore in this paper is Syllable Contact, which was first stated as the Syllable Contact Law by \citet{murray.vennemann.1983}:

\ex. ``The preference for a syllabic structure $A$\$$B$, where $A$ and $B$ are marginal segments and $a$ and $b$ are the Consonantal Strength
values of $A$ and $B$ respectively, increases with the value of $b$ minus $a$'' \citep{murray.vennemann.1983}

\citet{rose.2000} reformulates this as a violable, but categorical, constraint within the context of Optimality Theory and uses it in an analysis of Chaha sonority-driven epenthesis:

\ex.  \textsc{SyllCon}: The first segment of the onset of a syllable must be lower in sonority than the last segment in the immediately preceding syllable.

More recently, Syllable Contact has been recast as a gradient family of constraints, for example by \citet{gouskova.2002, gouskova.2004}.  She defines the distance {\sc Dis} between two consonants in a syllable contact situation as the sonority of the second minus the sonority of the first.  For example, [t.s] = +1 if [s] and [t] are only one step apart on a sonority scale.  She then defines the following family of constraints:

\ex. {\sc *Dis-}$n$: Assign a violation mark if the {\sc Dis} between two adjacent heterosyllabic consonants is $n$ (adapted from \citep{gouskova.2002})

This gives rise to a universal hierarchy:

\ex. {\sc *Dis+7} $\gg$ {\sc *Dis+6} $\gg$ ... {\sc *Dis+0} $\gg$ {\sc *Dis-1} $\gg$ ... {\sc *Dis-7}.

Thus heterosyllabic clusters that rise sharply in sonority -- that have a high {\sc Dis} -- are more marked than more falling clusters.

The predicted hierarchy of susceptibility to epenthesis of the clusters is as follows:

\ex. Syllable Contact hierarchy (based on {\sc *Dis}):

\vspace{-3em}
\noindent \resizebox{\linewidth}{!}{\usebox{\syllablecontacthierarchy}}

Syllable Contact applies only across syllable boundaries.  Therefore, when sonority-driven epenthesis occurs in onsets or codas, other sonority-based markedness constraints must be employed.  One such is {\sc Sonority Sequencing}, which we will see in the context of Rose's analysis in the next section.
